---
title: "Exploration"
author: "Neeraj Sharma"
date: "5/24/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r}
library(tidyverse)
library(here)
library(stargazer)
library(knitr)
library(ggthemes)
library(kableExtra)
library(lubridate)
library(scales)
```

```{r}
crashes <- read_csv(here("Data", "Crashes.csv"))
person <- read_csv(here("Data", "Person.csv"))
vehicles <- read_csv(here("Data", "Vehicles.csv"))
priority_intersections <- read_csv(here("Data", "Priority_Intersections.csv"))
street_improvement_projects_intersections <- read_csv(here("Data", "SIP_Intersections.csv"))
speed_humps <- read_csv(here("Data", "Speed_Humps.csv"))

lucas_v3 <- read_csv(here("Data", "Lucas Data", "regressions_v3_new.csv")) %>% 
  select(-COLLISION_ID)
```

# Verifying Lucas's Regressions

```{r}
lucas_v3

lm(count ~ bumps + month + speed_reduction, data = lucas_v3) %>% 
  summary()

stargazer(lm(count ~ bumps + month + speed_reduction, data = lucas_v3))
```

Things I want to know now:
* Where has there been treatment for me to do a diff-in-diff on?
* What different treatments have been done?
* I'm not seeing great before/after visually. 

## Where is the missing zip code info located?

In total there are `r crashes %>% drop_na("ZIP CODE") %>% nrow()` crashes with Zipcode information. This is pretty good for a raw dataset 1.7 million crashes.

```{r}
crashes %>%
  filter(is.na(`ZIP CODE`)) %>%
  group_by(`ON STREET NAME`) %>%
  count() %>%
  arrange(desc(n)) %>%
  head(10) %>%
  kable()
```

## Where are most crashes located?

```{r}
crashes %>%
  count(BOROUGH) %>%
  ggplot(aes(x = fct_reorder(BOROUGH, -n), y = n)) +
  geom_col() +
  scale_y_continuous(labels = comma)
```

## What are the most dangerous intersections?

Most crashes take place on on the Parkways/expressways. I have removed them here so we are just looking at actual intersections. 

```{r}
crashes %>% 
  group_by(`ON STREET NAME`, `CROSS STREET NAME`, `BOROUGH`) %>% 
  summarize(crash_count = n()) %>% 
  drop_na(`CROSS STREET NAME`) %>% 
  arrange(desc(crash_count)) %>% 
  head(10) %>% 
  kable()
```

Let's take ROCKAWAY BOULEVARD	BROOKVILLE BOULEVARD and see how it has changed over time.

```{r}
crashes %>% 
  filter(`ON STREET NAME` == "ROCKAWAY BOULEVARD" & `CROSS STREET NAME` == "BROOKVILLE BOULEVARD") %>% 
  mutate(`CRASH DATE` = mdy(`CRASH DATE`)) %>% 
  group_by(month = floor_date(`CRASH DATE`, "quarter")) %>% 
  summarize(count = n()) %>% 
  ggplot(aes(x = month, y = count)) + 
  geom_line() + 
  labs(title = "Quarterly crashes at Rockaway/Brookville over time", x = "Date")

top_causes_rockaway_brookville <- crashes %>% 
  filter(`ON STREET NAME` == "ROCKAWAY BOULEVARD" & `CROSS STREET NAME` == "BROOKVILLE BOULEVARD") %>% 
  count(`CONTRIBUTING FACTOR VEHICLE 1`) %>% 
  arrange(desc(n)) %>% 
  head(7) 

top_causes_rockaway_brookville %>% 
  ggplot(aes(x = fct_reorder(`CONTRIBUTING FACTOR VEHICLE 1`, -n), y = n)) +
  geom_col() +
  labs(title = "Top 7 causes of accident at Rockaway/Brookville over time")


crashes %>% 
  filter(`ON STREET NAME` == "ROCKAWAY BOULEVARD" & `CROSS STREET NAME` == "BROOKVILLE BOULEVARD") %>% 
  mutate(`CRASH DATE` = mdy(`CRASH DATE`)) %>% 
  group_by(month = floor_date(`CRASH DATE`, "quarter"), `CONTRIBUTING FACTOR VEHICLE 1`) %>%
  summarize(count = n()) %>% 
  semi_join(top_causes_rockaway_brookville) %>% 
  ggplot(aes(x = month, y = count, color = `CONTRIBUTING FACTOR VEHICLE 1`)) + 
  geom_line()
```

Let's take a look at Manhattan's most dangerous zone. EAST 59 STREET/2 AVENUE	

```{r}
crashes %>% 
  filter(`ON STREET NAME` == "EAST 59 STREET" & `CROSS STREET NAME` == "2 AVENUE") %>% 
  mutate(`CRASH DATE` = mdy(`CRASH DATE`)) %>% 
  group_by(month = floor_date(`CRASH DATE`, "quarter")) %>% 
  summarize(count = n()) %>% 
  ggplot(aes(x = month, y = count)) + 
  geom_line() + 
  labs(title = "Quarterly crashes at EAST 59 STREET/Brookville over time", x = "Date")

top_causes_59_2 <- crashes %>% 
  filter(`ON STREET NAME` == "EAST 59 STREET" & `CROSS STREET NAME` == "2 AVENUE") %>% 
  count(`CONTRIBUTING FACTOR VEHICLE 1`) %>% 
  arrange(desc(n)) %>% 
  head(7) 

top_causes_59_2 %>% 
  ggplot(aes(x = fct_reorder(`CONTRIBUTING FACTOR VEHICLE 1`, -n), y = n)) +
  geom_col() +
  labs(title = "Top 7 causes of accident at EAST 59 STREET/2nd ave over time")


crashes %>% 
  filter(`ON STREET NAME` == "EAST 59 STREET" & `CROSS STREET NAME` == "2 AVENUE") %>% 
  mutate(`CRASH DATE` = mdy(`CRASH DATE`)) %>% 
  group_by(month = floor_date(`CRASH DATE`, "quarter"), `CONTRIBUTING FACTOR VEHICLE 1`) %>%
  summarize(count = n()) %>% 
  semi_join(top_causes_59_2) %>% 
  ggplot(aes(x = month, y = count, color = `CONTRIBUTING FACTOR VEHICLE 1`)) + 
  geom_line()
```

Specific intersections aren't yielding enough for me. Let me do boroughs broadly. 

```{r}
important_crash_reasons <- crashes %>%
  filter(`CONTRIBUTING FACTOR VEHICLE 1` != "Unspecified") %>% 
  count(`CONTRIBUTING FACTOR VEHICLE 1`) %>% 
  slice_max(`n`, n = 5)
            
crashes %>% 
  mutate(`CRASH DATE` = mdy(`CRASH DATE`)) %>% 
  group_by(quarter = floor_date(`CRASH DATE`, "quarter"), `BOROUGH`, `CONTRIBUTING FACTOR VEHICLE 1`) %>% 
  summarize(count = n()) %>% 
  semi_join(important_crash_reasons) %>% 
  ggplot(aes(x = quarter, y = count, color = `CONTRIBUTING FACTOR VEHICLE 1`)) + 
  geom_line() + 
  facet_wrap(~BOROUGH, scales = "free_y") +
  labs(title = "Number of Accidents by Cause Across Boroughs",
       subtitle = "2012 to Present",
       color = "Crash Reason",
       x = "Quarter", y = "Number of Accidents") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = -25, hjust = 0), 
        plot.background = element_rect(fill = "lightblue"),
        plot.margin = margin(r = 2, unit = "cm"), 
        legend.position = "bottom") +
  guides(color=guide_legend(nrow=2,byrow=TRUE))
```

Questions this creates for me:
* Do numbers go up in mid 2014 and stuff because their data reporting became more complete or were there actually more accidents as a result of those?

## Let's hand calcualte some KSI's for intersections

```{r}
crashes %>%
  rename(date = `CRASH DATE`, time = `CRASH TIME`, borough = BOROUGH, 
         injured = `NUMBER OF PERSONS INJURED`, killed = `NUMBER OF PERSONS KILLED`, 
         main_factor = `CONTRIBUTING FACTOR VEHICLE 1`, vehicle_1 = `VEHICLE TYPE CODE 1`,
         street = `ON STREET NAME`, cross = `CROSS STREET NAME`) %>% 
  mutate(date = mdy(date)) %>%
  # filter(date < ymd(20151231)) %>% 
  group_by(street, cross, borough) %>% 
  summarize(count_inj = sum(injured), count_kill = sum(killed)) %>% 
  mutate(ksi = count_inj + count_kill) %>% 
  drop_na(cross, borough) %>% 
  arrange(desc(ksi)) %>% 
  ungroup() %>% 
  group_by(borough) %>% 
  mutate(ranking_in_borough = row_number(), 
         running_ksi = cumsum(ksi), 
         total_ksi_in_borough = sum(ksi, na.rm = TRUE),
         priority_area = if_else(running_ksi < 0.15*total_ksi_in_borough, 1, 0))
```

## Let us check how treatment is implimented?

Do we have strict exogeniety violations? We def have violations across all million crashes/interventions, and then in the top most frequent ones. But what about the intersections that are dangerous, but not that dangerous? Does NYC truely go sequentially or just randomly fix, lets say, the 50th to 150th most commonly dangerous intersections. If they randomly fix, then we have satisfied strict exogeniety for that sample and can test. 

```{r}
priority_intersections
street_improvement_projects_intersections
```

## Gonna do some random regressions

```{r}
cleaned_crashes <- crashes %>% 
  select(date = `CRASH DATE`, time = `CRASH TIME`, borough = BOROUGH, injured = `NUMBER OF PERSONS INJURED`,
         killed = `NUMBER OF PERSONS KILLED`, main_factor = `CONTRIBUTING FACTOR VEHICLE 1`, vehicle_1 = `VEHICLE TYPE CODE 1`) %>%
  mutate(manhattan = ifelse(borough == "MANHATTAN", 1, 0),
         brooklyn = ifelse(borough == "Brooklyn", 1, 0),
         bronx = ifelse(borough == "BRONX", 1, 0),
         staten = ifelse(borough == "STATEN ISLAND", 1, 0),
         queens = ifelse(borough == "QUEENS", 1, 0),
         )

cleaned_crashes %>%
  count(vehicle_1) %>% arrange(desc(n))

# glm(injured ~ manhattan + bronx + staten + queens, family = "binomial", data = cleaned_crashes) %>% 
#   summary()


```

## Let's consider accidents with pedestrians

```{r}
cleaned <- crashes %>%
  rename(date = `CRASH DATE`, time = `CRASH TIME`, borough = BOROUGH, 
         persons_injured = `NUMBER OF PERSONS INJURED`, persons_killed = `NUMBER OF PERSONS KILLED`, 
         peds_injured = `NUMBER OF PEDESTRIANS INJURED`, peds_killed = `NUMBER OF PEDESTRIANS KILLED`, 
         cycl_injured = `NUMBER OF CYCLIST INJURED`, cycl_killed = `NUMBER OF CYCLIST KILLED`,
         main_factor = `CONTRIBUTING FACTOR VEHICLE 1`, vehicle_1 = `VEHICLE TYPE CODE 1`,
         street = `ON STREET NAME`, cross = `CROSS STREET NAME`) %>% 
  mutate(date = mdy(date))

cleaned %>% 
  filter(peds_injured >= 1) %>% 
  group_by(borough, peds_injured, quarter = floor_date(date, "quarter")) %>% 
  summarize(count = n()) %>% 
  ggplot(aes(x = quarter, y = count, color = factor(peds_injured))) + 
  geom_line() + 
  facet_wrap(~borough) +
  labs(title = "Count of accidents causing injury to Peds over time",
       subtitle = "despite seeing more accidents, the dangerous/injuring accidents are down")
```

## Let's make a similar graph, but with deaths instead of injuries

```{r}
cleaned %>% 
  filter(peds_killed >= 1) %>% 
  group_by(borough, peds_killed, quarter = floor_date(date, "quarter")) %>% 
  summarize(count = n()) %>% 
  ggplot(aes(x = quarter, y = count, color = factor(peds_killed))) + 
  geom_line() + 
  facet_wrap(~borough) +
  labs(title = "Count of accidents causing injury to Peds over time")
```

This is a little more confusing, mostly cuz pedestrian deaths are such a low frequency event.You do see subtle trends downwards in Manhattan and the Bronx maybe based on what I see.

## Same analysis for cyclists

```{r}
cleaned %>% 
  filter(cycl_injured >= 1) %>% 
  group_by(borough, cycl_injured, quarter = floor_date(date, "quarter")) %>% 
  summarize(count = n()) %>% 
  ggplot(aes(x = quarter, y = count, color = factor(cycl_injured))) + 
  geom_line() + 
  facet_wrap(~borough) +
  labs(title = "Count of accidents causing injury to cyclists over time")

cleaned %>% 
  filter(cycl_killed >= 1) %>% 
  group_by(borough, cycl_killed, quarter = floor_date(date, "quarter")) %>% 
  summarize(count = n()) %>% 
  ggplot(aes(x = quarter, y = count, color = factor(cycl_killed))) + 
  geom_line() + 
  facet_wrap(~borough) +
  labs(title = "Count of accidents causing killed to cyclists over time")
```

# When pedestrians are injured, what is it that kills them?

what kills them

```{r}
ped_killers <- cleaned %>% 
  filter(peds_injured >= 1) %>% 
  group_by(main_factor) %>% 
  summarize(count = n()) %>% 
  arrange(desc(count))

cleaned %>% 
  filter(peds_injured >= 1)
```

## Let's check out speed humps

```{r}
# speed_humps %>% 
#   mutate(date = ymd(date_insta))
```

## Let's merge all the data together and see what we can get?

Are the incident ID's uniform?

```{r}
# full_data <- inner_join(crashes, person, by = c("COLLISION_ID")) %>%
#   inner_join(vehicles %>% select(-VEHICLE_ID), by = c("COLLISION_ID"))
# 
# full_data %>% head(10)
```

## These are the graphs I made for the presentation deck

```{r}
cleaned %>% 
  drop_na(borough) %>% 
  group_by(borough, main_factor) %>% 
  summarize(count = n()) %>% 
  filter(main_factor != "Unspecified") %>% 
  slice_max(`count`, n = 5) %>% 
  ggplot(aes(x = fct_reorder(main_factor, -count), y = count)) +
  geom_col() +
  facet_wrap(~borough, scales = "free_x") + 
  labs(title = "Number of Accidents by Cause Across Boroughs",
       subtitle = "2012 to Present",
       x = "Cause of Collision", y = "Number of Accidents") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = -25, hjust = 0), 
        plot.background = element_rect(fill = "lightblue"),
        plot.margin = margin(r = 2, unit = "cm"))


main_factor_of_crashes_inBoroughs <- cleaned %>% 
  drop_na(borough) %>% 
  group_by(borough, main_factor) %>% 
  summarize(count = n()) %>% 
  filter(main_factor != "Unspecified") %>% 
  slice_max(`count`, n = 5) %>% 
  select(-count)

cleaned %>% 
  drop_na(borough) %>% 
  mutate(pre2015 = ifelse(date > ymd(20151231), "Post", "Pre")) %>%
  group_by(borough, main_factor, pre2015) %>% 
  summarize(count = n()) %>% 
  filter(main_factor != "Unspecified") %>% 
  inner_join(main_factor_of_crashes_inBoroughs) %>% 
  ggplot(aes(x = fct_reorder(main_factor, -count), y = count, fill = factor(pre2015, levels = c("Pre", "Post")))) +
  geom_col(position = "dodge2") +
  facet_wrap(~borough, scales = "free_x") + 
  labs(title = "Number of Accidents by Cause Across Boroughs",
       subtitle = "2012 to End 2015, 2016 to Present",
       x = "Cause of Collision", y = "Number of Accidents",
       fill = "Pre/Post 2015") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = -25, hjust = 0), 
        plot.background = element_rect(fill = "lightblue"),
        plot.margin = margin(r = 2, unit = "cm"), 
        legend.position = c(0.95, 0.1))
```

```{r}
# street_improvement_projects_intersections %>%
#   mutate(the_geom = str_extract_all(the_geom, "\\([^()]+\\"))
  
  
  # mutate(LONG = str_extract_all(the_geom, "[0-9]+.[0-9]+")) %>% unnest()
```
